HPC--101 -- Cheatsheet \vspace{-2ex}

### 2016-01-22 hpc_101/cheatsheet/paper.tex
style changes

\begin{document}
\setlength{\droptitle}{-10em}
\title{HPC--101 -- Cheatsheet \vspace{-2ex}}
\date{\today}
\author{Sean Cleveland Ph.D, Ron Merrill Ph.D,\\David Schanzenbach M.S.\\~\\University of {\hawaii}\\Information Technology Services -- {\ci}}
\maketitle
\section{Directory Navigation}
\begin{itemize}
\item[] cd {\pth{Directory}}\desc{Change to directory specified}
\item[] ls {\pth{Path}}\desc{List the contents of the specified path}
\item[] ls -l {\pth{Path}}\desc{This flag list the paths content in long form}
\item[] ls -lh {\pth{Path}}\desc{Make the filesize humanreable}
\item[] ls -a {\pth{Path}}\desc{Show hidden directories and files}
%\item[] pwd \desc{Print working directory}
\end{itemize}

\section{SSH/SCP}
\begin{itemize}
\item ssh {\lft}user{\rht}@{\lft}host{\rht}
\item ssh -Y {\lft}user{\rht}@{\lft}host{\rht}\desc{Enable X11 forwarding}
\item scp~{\lft}file{\rht}~{\lft}user{\rht}@{\lft}host{\rht}:{\lft}remote~path{\rht}\desc{Copy a file to a remote location}
\item scp~-r~{\lft}dir{\rht}~{\lft}user{\rht}@{\lft}host{\rht}:{\lft}remote~path{\rht}\desc{Recursivly copy a directory to a remote location}
\end{itemize}

\section{SLURM}
\subsection{Management And Monitoring}
\begin{itemize}
\item[] sbatch \pth{slurm\_script}\desc{Submit a slurm script to the scheduler for batch processing}
\item[] sbatch~--array=[\#-\#]~\pth{slurm\_script}\desc{Submit a job array to the scheduler}
\item[] srun \desc{Used in submitting an interactive job, or also  used within a slurm\_script}
\item[] srun.x11 \desc{Used in submitting an interactive job, that also forwards the X, if you logged in while enabling X forwarding}
\item{} squeue \desc{Display all jobs running or waiting on the cluster}
\item{} squeue -u{\lft}user{\rht} \desc{Only display jobs for the specified user}
\item{} sinfo \desc{Display the partitions and nodes state}
\item{} scancel {\lft}jobid{\rht} \desc{Cancel the specified job}
\end{itemize}

\subsection{Details and Profiling}
\begin{itemize}
\item[] scontrol show jobid {\lft}jobid{\rht}\desc{Show job details of a waiting or running job}
\item[] scontrol show parition {\lft}partition name{\rht}\desc{Show details of the specified partition}
\item[] scontrol show node {\lft}node name{\rht}\desc{Show details of the specified node}
\item[] sacct -l -j {\lft}jobid{\rht}\desc{Show usage details of a job}
\item[] sacct -u {\lft}user{\rht}\desc{Show all jobs from a given user}
\end{itemize}

\section{Miscellaneous}
\subsection{Commands}
\begin{itemize}
\item[] less \pth{file} \desc{Show contents of file\\Navigate using up/down arrow keys, spacebar, or pageup/pagedown keys\\  Press 'q' to exit out of less}
\item[] less -S \pth{file} \desc{Show contents of file without line wrap\\Navigate using up/down arrow keys, spacebar, or pageup/pagedown keys\\Press 'q' to exit out of less}

\end{itemize}

\subsection{Operators}
\begin{itemize}
\item[] | \desc{Pipe operator is used between two commands, in which you wish to pass the output of the 1st command to the input of the 2nd command\\Ex. \texttt{sacct -l -j 467 | less -S }}
\end{itemize}

\subsection{Hosts}
\begin{itemize}
\item[] login-0001 -- uhhpc1.its.hawaii.edu
\item[] login-0002 -- uhhpc2.its.hawaii.edu
\end{itemize}

\subsection{Globus Endpoints}
\begin{itemize}
\item[] login-0001 -- hawaii#UHHPC1
\item[] login-0002 -- hawaii#UHHPC2
\end{itemize}

>>>>

\begin{document}
\setlength{\droptitle}{-10em}
\title{HPC--101 -- Cheatsheet \vspace{-2ex}}
\date{\today}
\author{Sean Cleveland Ph.D, Ron Merrill Ph.D,\\David Schanzenbach M.S.\\~\\University of {\hawaii}\\Information Technology Services -- {\ci}}
\maketitle
\section{Directory Navigation}
\begin{itemize}
\item[] \texttt{cd {\pth{Directory}}}\desc{Change to directory specified}
\item[] \texttt{ls {\pth{Path}}}\desc{List the contents of the specified path}
\item[] \texttt{ls -l {\pth{Path}}}\desc{This flag list the paths content in long form}
\item[] \texttt{ls -lh {\pth{Path}}}\desc{Make the filesize humanreable}
\item[] \texttt{ls -a {\pth{Path}}}\desc{Show hidden directories and files}
%\item[] pwd \desc{Print working directory}
\end{itemize}

\section{SSH/SCP}
\begin{itemize}
\item \texttt{ssh {\lft}user{\rht}@{\lft}host{\rht}}
\item \texttt{ssh -Y {\lft}user{\rht}@{\lft}host{\rht}}\desc{Enable X11 forwarding}
\item \texttt{scp~{\lft}file{\rht}~{\lft}user{\rht}@{\lft}host{\rht}:{\lft}remote~path{\rht}}\desc{Copy a file to a remote location}
\item \texttt{scp~-r~{\lft}dir{\rht}~{\lft}user{\rht}@{\lft}host{\rht}:{\lft}remote~path{\rht}}\desc{Recursivly copy a directory to a remote location}
\end{itemize}

\section{SLURM}
\subsection{Management And Monitoring}
\begin{itemize}
\item[] \texttt{sbatch \pth{slurm\_script}}\desc{Submit a slurm script to the scheduler for batch processing}
\item[] \texttt{sbatch~--array=[\#-\#]~\pth{slurm\_script}}\desc{Submit a job array to the scheduler}
\item[] \texttt{srun} \desc{Used in submitting an interactive job, or also  used within a slurm\_script}
\item[] \texttt{srun.x11} \desc{Used in submitting an interactive job, that also forwards the X, if you logged in while enabling X forwarding}
\item{} \texttt{squeue} \desc{Display all jobs running or waiting on the cluster}
\item{} \texttt{squeue -u{\lft}user{\rht}} \desc{Only display jobs for the specified user}
\item{} \texttt{sinfo} \desc{Display the partitions and nodes state}
\item{} \texttt{scancel {\lft}jobid{\rht}} \desc{Cancel the specified job}
\end{itemize}

\subsection{Details and Profiling}
\begin{itemize}
\item[] \texttt{scontrol show jobid {\lft}jobid{\rht}}\desc{Show job details of a waiting or running job}
\item[] \texttt{scontrol show parition {\lft}partition name{\rht}}\desc{Show details of the specified partition}
\item[] \texttt{scontrol show node {\lft}node name{\rht}}\desc{Show details of the specified node}
\item[] \texttt{sacct -l -j {\lft}jobid{\rht}}\desc{Show usage details of a job}
\item[] \texttt{sacct -u {\lft}user{\rht}}\desc{Show all jobs from a given user}
\end{itemize}

\section{Miscellaneous}
\subsection{Commands}
\begin{itemize}
\item[] \texttt{less \pth{file}} \desc{Show contents of file\\Navigate using up/down arrow keys, spacebar, or pageup/pagedown keys\\  Press 'q' to exit out of less}
\item[] \texttt{less -S \pth{file}} \desc{Show contents of file without line wrap\\Navigate using up/down arrow keys, spacebar, or pageup/pagedown keys\\Press 'q' to exit out of less}
\end{itemize}
\bigskip
\subsection{Operators}
\begin{itemize}
\item[] \texttt{|} \desc{Pipe operator is used between two commands, in which you wish to pass the output of the 1st command to the input of the 2nd command\\Ex. \texttt{sacct -l -j 467 | less -S }}
\end{itemize}

\subsection{Hosts}
\begin{itemize}
\item[] login-0001 -- \texttt{uhhpc1.its.hawaii.edu}
\item[] login-0002 -- \texttt{uhhpc2.its.hawaii.edu}
\end{itemize}

\subsection{Globus Endpoints}
\begin{itemize}
\item[] login-0001 -- \texttt{hawaii#UHHPC1}
\item[] login-0002 -- \texttt{hawaii#UHHPC2}
\end{itemize}
